Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-10 Final Draft/Final Draft.Rmd
some writing

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
short: ""
journal: "" # AER, AEJ, PP, JEL
month: "`r format(Sys.Date(), '%m')`"
year: "`r format(Sys.Date(), '%Y')`"
vol: 1
issue: 1
jel:
  - 
  -
keywords:
  - 
  - 
author:
  - name: Catherine Darin
    firstname: Catherine
    surname: Darin
    email: cdarin@hks.harvard.edu
    affiliation: Harvard University
  - name: Zagreb Mukerjee
    firstname: Zagreb
    surname: Mukergee
    email: zagrebmukerjee@fas.harvard.edu
    affiliation: Harvard University
acknowledgements: 
abstract: |
  What led to Donald Trump's surprising 2016 election victory? This paper examines the potential contribution of deindustrialization. Counties differ by exposure to manufacturing, which we use in an instrumental-variable approach to identify the effect of manufacturing job loss on change in Democratic vote share. We find that Democratic vote share falls in counties with high manufacturing job loss since 2004. Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites. This suggests a racial component to how voters process economic hardship.
output: rticles::aea_article
---

>>>>

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
short: ""
journal: "" # AER, AEJ, PP, JEL
month: "`r format(Sys.Date(), '%m')`"
year: "`r format(Sys.Date(), '%Y')`"
vol: 1
issue: 1
author:
  - name: Catherine Darin
    firstname: Catherine
    surname: Darin
    email: cdarin@hks.harvard.edu
    affiliation: Harvard University
  - name: Zagreb Mukerjee
    firstname: Zagreb
    surname: Mukerjee
    email: zagrebmukerjee@fas.harvard.edu
    affiliation: Harvard University
acknowledgements: 
abstract: |
  What led to Donald Trump's surprising 2016 election victory? This paper examines the potential contribution of deindustrialization. Counties differ by exposure to manufacturing, which we use in an instrumental-variable approach to identify the effect of manufacturing job loss on change in Democratic vote share. We find that Democratic vote share falls in counties with high manufacturing job loss since 2004. Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites. This suggests a racial component to how voters process economic hardship.
output: rticles::aea_article
---

\section{Data and Methods}

\subsection{Data}

Following \cite{BW}, our unit of analysis is the county. This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy. The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016. We obtain this from XXXXXXXXX

We want to measure the causal relationship between deindustrialization and the change in vote share. As a measure of deindustrialization, we use the destruction of manufacturing jobs, as a share of the total manufacturing
